A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2017-05-18 meth.tex
adding methods section with table

\begin{table}[]
\centering
\caption{All Harmonization Methods Provided in \code{aneris}}
\label{my-label}
\begin{tabular}{|l|l|l|}
\hline
Method Name                             & Harmonization Type & Convergence Year\\
\hline
\code{constant\_ratio}                  & ratio              & $t_f = \infty$\\
\code{reduce\_ratio\_<year>}            & ratio              & $t_f = $\code{<year>}\\
\code{constant\_offset}                 & offset             & $t_f = \infty$\\
\code{reduce\_offset\_<year>}           & offset             & $t_f = $\code{<year>}\\
\code{linear\_interpolate\_<year>}      & interpolation      & $t_f = $\code{<year>}\\
\hline
\end{tabular}
\end{table}

@@

>>>>

\begin{table}[]
\centering
\caption{All Harmonization Methods Provided in \code{aneris}}
\label{tab:meths}
\begin{tabular}{|l|l|l|}
\hline
Method Name                             & Harmonization Type & Convergence Year\\
\hline
\code{constant\_ratio}                  & ratio              & $t_f = \infty$\\
\code{reduce\_ratio\_<year>}            & ratio              & $t_f = $\code{<year>}\\
\code{constant\_offset}                 & offset             & $t_f = \infty$\\
\code{reduce\_offset\_<year>}           & offset             & $t_f = $\code{<year>}\\
\code{linear\_interpolate\_<year>}      & interpolation      & $t_f = $\code{<year>}\\
\hline
\end{tabular}
\end{table}

@@

\subsection{\code{aneris} Workflow}

The full \code{aneris} workflow is comprised of a number of components shown
graphically in Figure \ref{fig:workflow}. Unharmonized model data and
run-control configuration are read in via an Excel spreadsheet. Data is assumed
to be in the \textit{IAM Consortium} format, i.e., using \code{Model},
\code{Scenario}, \code{Region}, \code{Variable}, and \code{Unit} columns in
addition to column representing each modeled time period. Users are able to
control the harmonization process via a number of controls. First, users can
provide \textit{override} methods for any combination of region and variable. If
override methods are provided, they are used instead of the default methods as
determined by the default method decision tree. Further, users can set the
above-mentioned thresholds as well as the LUC method used in the decision
tree. Further detail of input parameters can be found at
\hyperlink{http://aneris.readthedocs.io/en/latest/}.

\begin{figure}
  \begin{center}
    \includegraphics[height=0.85\textheight]{aneris-workflow.pdf}
    \caption[]{
      \label{fig:workflow}
      The full harmonization process as executed by \code{aneris}. Operations
      that can be configured with user-based input configurations are shown in
      purple. The core harmonization process is shown in orange.  }
  \end{center}
\end{figure}

Input data then undergoes a cleaning operation, which adds any trajectories in
the historical dataset but not provided by the model and detects any issues that
would cause the harmonization process to fail. The methods used to harmonize the
data are then determined and the harmonization process is executed. Upon
completion of the harmonization process, aggregation of common analysis regions
is performed (e.g., the 5 RCP regions \TODO{CITE}). Finally, any exogenous
trajectories the user provides are added. Exogenous trajectories are normally
provided for unmodeled gases with well-accepted scenario trajectories, e.g.,
Chlorofloro Carbons provided by WMO \TODO{CITE}. Upon completion, the harmonized
trajectories and metadata regarding the harmonization process are returned. A
description of all returned metadata is provided in Table \ref{tab:metadata}.

\begin{table}[]
\centering
\caption{Metadata provided by the \code{aneris} harmonization routine. This metadata is provided for every combination of region, sector, and emissions species.}
\label{my-tab:metadata}
\begin{tabular}{|p{2cm}|p{8cm}|}
\hline
Column       & Description                                                                  \\
\hline
\hline
method       & The harmonization method used.                                               \\
\hline
default      & The default harmonization method as determined by the default decision tree. \\
\hline
override     & The method provided as an override (if any).                                 \\
\hline
offset       & The offset value between history and model in the harmonization year.        \\
\hline
ratio        & The ratio value between history and model in the harmonization year.         \\
\hline
cov          & The covariance value of the historical trajectory.                           \\
\hline
unharmonized & The unharmonized value in the harmonization year.                            \\
\hline
history      & This historical value in the harmonization year.                             \\
\hline
harmonized   & The resulting harmonized value in the harmonization year.\\
\hline
\end{tabular}
\end{table}
